Exploring the Composition of Lithic Assemblages in Mesolithic South-Eastern Norway

### 2022-01-20 analysis/paper/paper.Rmd
Minor adjustment following peer review

Thus, while some secondary expectations of the WABI as related to cores and blanks do not seem to apply to the present material, it is difficult to say to what degree this is caused by idiosyncrasies in the Norwegian system for classification of lithics and properties of the lithic material itself. The relationship between VDL and RFSL does correspond to the model and follows a clear temporal trend that is also correlated with the increased use of local raw material. Thus, if the relationship between VDL and RFSL is accepted as a proxy for curation, and is related to land-use and mobility patterns, these findings would be in line with previous research into the Mesolithic of Norway, indicating that earlier sites are associated with higher degree of mobility than sites from later phases [e.g. @bergsvik2001; @bjerck2008; @glørstad2010; @jaksland2001]. To explore this proposition further, these two variables are subjected to more detailed scrutiny below.

>>>>

Thus, while the relative frequency of blades and cores does not appear to meet the expectations of the WABI, it is difficult to say to what degree this is caused by idiosyncrasies in the Norwegian system for classification of lithics and properties of the lithic material itself. The relationship between VDL and RFSL does correspond to the model and follows a clear temporal trend that is also correlated with the increased use of local raw material. Thus, if the relationship between VDL and RFSL is accepted as a proxy for curation, and is related to land-use and mobility patterns, these findings would be in line with previous research into the Mesolithic of Norway, indicating that earlier sites are associated with higher degree of mobility than sites from later phases [e.g. @bergsvik2001; @bjerck2008; @glørstad2010; @jaksland2001]. To explore this proposition further, these two variables are subjected to more detailed scrutiny below.
